sdmTMB: Fast, flexible, and user-friendly spatial and spatiotemporal generalized linear mixed-effects models

### 2021-11-02 doc/paper.Rmd
Outline structure

@@

<!-- Paragraph on derived quantities here-->
The results from a model fit with sdmTMB can be used to generate quantities of interest.
For example, sdmTMB provides functionality for generating population-level summaries for each time slice including fraction of area occupied (TODO?), 2-dimensional center of gravity (`sdmTMB::get_cog()`), and total population index (`sdmTMB::get_index()`).
Estimated parameters from the Matérn covariance function can be used to describe the marginal spatial variance and Matérn range (distance at which spatial correlation decays to $\sim$ 0.13).

>>>>

- high-level paragraph or two about what the model includes, referencing Fig 1
- high-level paragraph about design philosophy (modular [separate predict, residuals, etc.], familiar/clear naming, expensive computations only if needed, work with regular data frames, ...?)
- high-level paragraph about simulation capabilities and + testing performed (reference supplement)
- model selection/cross validation paragraph
- derived quantities paragraph (or just put this in the examples?)

- example 1 + figs
- example 2 + figs

- discussion
    - take home, re-iterate
    - how to pick among packages/tools including a bit outside the SPDE world? (table)
    - touch on other stuff possible: priors, Bayes, barrier meshes, residuals, 
      simulation from joint precision, ...?

@@

<!-- Paragraph on derived quantities here-->
The results from a model fit with sdmTMB can be used to generate quantities of interest.
For example, sdmTMB provides functionality for generating population-level summaries for each time slice including the center of gravity (`sdmTMB::get_cog()`) and total population index (`sdmTMB::get_index()`).
Estimated parameters from the Matérn covariance function can be used to describe the marginal spatial variance and Matérn range (distance at which spatial correlation decays to $\sim$ 0.13).
